Incentivizing Exploration with Unbiased History

### 2018-10-22 2level.tex
2level

%!TEX root = main.tex
\section{Warm-up:  Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a sublinear regret
  rate. The policy essentially follows the ``explore-then-exploit''
  paradigm and consists two phases, which can be described as a
  two-level information graph (as shown in Figure~\ref{fig:2level}).
  In the first level, we perform exploration by simulating $T_1$
  independent runs \ALGG of $\GdT$ rounds. This is done by randomly
  dividing the first $T_1 \cdot \GdT$ agents into $T_1$ groups of
  equal size and each agent only observe the history of all previous
  agents in the same group.  In the second level, we ``exploit'' by
  showing all the remaining agents the entire history of first phase.

  The key idea behind the policy is that the first level effectively
  boosts the exploration probability of \ALGG. Since each run of \ALGG
  explores all arms with constant probability (Lemma
  \ref{lem:greedy}), by simulating multiple runs of \ALGG, we can
  ensure that with high probability, every arm is pulled with a
  sufficient number of times. As a result, every agent in the second
  level will pull an arm with mean rewards close to optimal.

@@

\begin{proof}
We will set $T_1$ later in the proof. For now, we just need to know we will make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this recommendation policy is symmetric over arms, we wlog assume that arm 1 has the highest mean in the proof.

The first $T_1 \cdot \GdT$ rounds will get total regret at most $T_1 \cdot \GdT$.  We focus on bounding the regret of the rest $T - T_1 \cdot \GdT$ rounds. We consider the following two clean events. We will first bound the probability that both of them happen and then we will show that they together imply upper bounds on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by agent $t$ and agent $t$ picks the arm with the highest $\hat{\mu}^t_a$.

\begin{itemize}
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:}

  For each arm $a$, define $q_a$ to be the expected number of arm $a$
  pulls in one run of \ALGG used in the first level.\swcomment{$q_a$
    probability or number?? the issue propagates downwards} 
    \jmcomment{$q_a$ is the expected number.}
    By Lemma
  \ref{lem:greedy}, we know $\GdP \leq q_a \leq
  \GdT$.\swcomment{$p_G T$?}
  \jmcomment{$q_a$ is only for one run of greedy. Not $T_1$ runs of greedy.}
   Define $W_1^a$ to be the event that the
  number of arm $a$ pulls in the first level is at least
  $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.\swcomment{what
    is the condition on $T_1$ and $T_G$ for this to hold?} 
    \jmcomment{$\GdT$ is a constant. This holds if $T_1 = \omega(\log(T))$ and $T$ is a larger than some constant.}
    By Chernoff
  bound,
\[
\Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\item  \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}

For each arm $a$, imagine there is a tape of $T$ arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agent pull arm $a$. Define $W^{a,t}_2$ to be the event that the empirical mean of the first $t$ pulls of arm $a$ is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the intersection of these events (i.e. $\bigcap_{a,t} W^{a,t}_2$).
By Chernoff bound,
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]
\end{itemize}

By union bound, we know $\Pr[W_1 \cap W_2] \geq 1 - 3/T$. Now we consider the case when $W_1 \cap W_2$ happens.

@@

Notice that if we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can set 
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
\end{proof}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

%!TEX root = main.tex
\section{Warm-up:  Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs \ALGG of $\GdT$
  rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and each agent only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

  The key idea behind the policy is that the first level effectively
  boosts the exploration probability of Greedy. Since each run of
  \ALGG explores all arms with constant probability (Lemma
  \ref{lem:greedy}), by simulating multiple runs of Greedy, we can
  ensure that with high probability, every arm is pulled with a
  sufficient number of times. As a result, every agent in the second
  level will pull an arm with mean rewards close to the optimal.

@@

\swcomment{I think this proof should go to appendix, so I didn't do
  too much refactoring}

\begin{proof}
  We will set $T_1$ later in the proof, depending on whether the gap
  parameter $\Delta$ is known. For now, we just need to know we will
  make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this policy is
  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
  has the highest mean.

  The first $T_1 \cdot \GdT$ rounds will get total regret at most
  $T_1 \cdot \GdT$.  We focus on bounding the regret from the second
  level of $T - T_1 \cdot \GdT$ rounds. We consider the following two
  clean events. We will first bound the probability that both of them
  happen and then we will show that they together imply upper bounds
  on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second
  level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by
  agent $t$ and agent $t$ picks the arm with the highest
  $\hat{\mu}^t_a$.

% \begin{itemize}
  \paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
  For each arm $a$, define $q_a$ to be the expected number of arm $a$
  pulls in a single run of \ALGG used in the first level.  By Lemma
  \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define $W_1^a$
  to be the event that the number of arm $a$ pulls in the first level
  is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.  \swedit{As long as
    we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$, this implies that
    the number of arm $a$ pulls is then at least $q_a T_1/2$.}  By
  Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\paragraph{Concentration of the empirical mean of arm $a$ pulls in the first level.}
To facilitate our reasoning, let us imagine there is a tape of length
$T$ for each arm $a$, with each cell containing an independent draw of
the realized reward from the distribution Ber$(\mu_a)$. Then for each
arm $a$ and any $N\in [T]$, we can think of the sequence of the first
$N$ realized rewards of $a$ coming from the prefix of $N$ cells in its
reward tape. Define $W^{a,t}_2$ to be the event that the empirical
mean of the first $t$ \swedit{realized rewards in the tape} of arm $a$
is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$
to be the intersection of these events (i.e.
$\bigcap_{a,t} W^{a,t}_2$).  By Chernoff bound,\swcomment{$t$ may be
  confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

By union bound, we know $\Pr[W_1 \cap W_2] \geq 1 - 3/T$. For the
remainder of the analysis, we will condition on the event
$W_1 \cap W_2$.

@@

Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.
\end{proof}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-10-22 model.tex
2level

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$.% \swcomment{do we plan to generalize to real-valued?}  
% \jmcomment{Probably not. We probably need some weird assumptions to make it work and we may need to change many parts of our proofs. The assumptions will be like: enough variance for anti-concentration and even more stuff for the greedy to has a small chance to work. Probably binary sound more natural and practical. And we should state something like binary should be interpreted as the feedback from the user, i.e. ``like'' or ``dislike''.}
At each round $t\in [T]$, a new agent $t$ arrives, receives a message
$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
reward $r_t\in \{0,1\}$ that is immediately observed by the
principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by
the agents, the \emph{regret} is defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]

>>>>

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$. At each round $t\in [T]$, a new agent $t$ arrives,
receives a message $m_t$ from the principal, chooses an arm
$a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is
immediately observed by the principal. Given any sequence of arms
$\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is
defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]
